### 2023-03-23 Documentation/WT group/NHL/Metodology/Metodology.tex
documentation

@@

>>>>

The classification is a key step in our routine. For being able to be used in multipurpose applications our classification routine must be able to run in real-time. Which means it must be fast and automatic classification.
Our goal is to improve and apply in our routine different approachs of non-visual spraying classification using the current data collected from the system.

@@

\begin{figure}[H]
    \centering
    \resizebox{50mm}{!}{\includegraphics{Figuras/report2/data3_sjaaksgraph2.png}}
    \caption{EHDA automation system setup}
    \label{fig:sjaaks_statistical_class}
\end{figure}

### 2023-03-23 Documentation/WT group/NHL/Results/Results.tex
documentation

\chapter{Results}

\subsection*{2.3 Manual experiments}

@@

    \begin{figure}[H]
        \center
        \includegraphics[width=12cm]{Figuras/report3/exp25-01-1.png}
        \caption{ exp25-01-1 (V x Q)}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=12cm]{Figuras/report3/exp-26-01-1.png}
        \caption{ exp-26-01-1 (V x Q)}
    \end{figure}

@@

\subsection*{2.4 Automatic experiments}

@@

\subsection*{2.5 Manual x Automatic Cone Jet stability island maps}

@@

\pagebreak

@@

>>>>

\chapter{Results}
\label{chap:Results}

\section{Classification}
\label{sec:classification_results}

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{Figuras/19:03/voltage_step.png}
    \caption{ exp-26-01-2 (V x Q)}
\end{figure}

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{Figuras/19:03/raw-data-example.png}
    \caption{ exp-26-01-2 (V x Q)}
\end{figure}

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{Figuras/19:03/classified-data-example.png}
    \caption{ exp-26-01-2 (V x Q)}
\end{figure}

\section{Map Sequence}
\label{sec:map_results}

\subsection{Manual experiments}

@@

@@

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{Figuras/regions.png}
    \caption{ exp-26-01-2 (V x Q)}
\end{figure}

\subsection{Automatic experiments}

@@

\subsection{Manual x Automatic Cone Jet stability island maps}

@@

@@

    \begin{figure}[H]
        \center
        \includegraphics[width=7cm]{Figuras/report4/map7-manual.png}
        \caption{ exp-26-01 manual classification}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=9cm]{Figuras/report4/map7-automatic-line.png}
        \caption{ exp-26-01 automatic classification}
    \end{figure}

\subsection{Non-dimensional axis}

\begin{figure}[H]
    \center
    \includegraphics[width=12cm]{Figuras/19:03/non-dimensional-1.png}
    \caption{ exp-26-01-2 (V x Q)}
\end{figure}

\section{Controller}
\label{sec:controller_results}

\subsection{Simple Controller}

Flowrate perturbation robustness test

\begin{figure}[H]
    \center
    \includegraphics[width=18cm]{Figuras/19:03/control_first_results.png}
    \caption{ exp-26-01-2 (V x Q)}
\end{figure}
